---
title: "Analysis"
author: "SW"
date: "7/28/2020"
output: pdf_document
---

```{r setup, comment=FALSE, warning=FALSE, results=FALSE, tidy=TRUE, message=FALSE}
library(tidyverse)
library(Hmisc)
library(nhanesA)
library(broom)
library(rstanarm)
library(brms)
library(nnet)
library(effects)
library(survey)
options(mc.cores = 4)
```

# Functions

```{r, comment=FALSE, warning=FALSE, results=FALSE, tidy=TRUE, message=FALSE}
th <- theme_classic() +
     theme(legend.title=element_text(size=18),
         legend.text=element_text(size=15),
         axis.text=element_text(size=15),
         axis.text.x=element_text(angle=90,vjust=.5),
         axis.title=element_text(size=25))

plot_vars <- function(usertype,outcome,vars=NULL,data){
  if (!is.null(vars)) vars <- sort(vars)
  
  data$users <- data[,usertype] %>% unlist()
  data$oc <- data[,outcome] %>% unlist()
  
  d <- data %>%
    filter(!is.na(oc),
           !is.na(bmicat),
           !is.na(users)) %>%
    distinct()
  
  if (is.null(vars)){
    d <- d %>%
      group_by(users,oc) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip()
  }else if (identical(vars,'ins')){
    d <- d %>%
      group_by(users,oc,ins) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_wrap(~ins)
  }else if (identical(vars,c('ins','sex'))){
    d <- d %>%
      group_by(users,oc,ins,sex) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins,sex) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_wrap(sex~ins)
  }else if (identical(vars,c('ins','race'))){
    d <- d %>%  
      group_by(users,oc,ins,race) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins,race) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_grid(race~ins)
  }else if (identical(vars,c('bmicat','ins'))){
    d <- d %>%  
      group_by(users,oc,ins,bmicat) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins,bmicat) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_grid(bmicat~ins)
  }else if (identical(vars,c('ins','race','sex'))){
    d <- d %>% 
      group_by(users,oc,ins,race,sex) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins,race,sex) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_grid(race ~ sex + ins)
  }else if (identical(vars,c('bmicat','ins','sex'))){
    d <- d %>%
      group_by(users,oc,ins,sex,bmicat) %>%
      dplyr::summarize(f=sum(wtintadj)) %>%
      group_by(users,ins,bmicat,sex) %>%
      mutate(f=f/sum(f)) %>%
      ggplot(aes(x=users,y=f,fill=oc)) +
      geom_col(color='black') +
      coord_flip() +
      facet_grid(bmicat ~ sex + ins)
  }
  d + labs(fill=outcome)
}

get_labs <- function(x, y) {
  labsx <- label(x)
  labsy <- label(y)
  overlap <- c(labsx[labsx != ''], labsy[labsy != ''])
  overlap <- overlap[!duplicated(overlap)]
  if (length(overlap) == 0)
    return(labsx)
  else
    return(overlap)
}

get_data <- function(query,
                     type = NULL,
                     translate = TRUE) {
  out <- NULL
  suffix <- c('', paste0('_', LETTERS[2:10]))
  yrs <- seq(1999, 1999 + 2 * length(suffix), 2)
  for (s in seq_along(suffix)) {
    qname <- paste0(query, suffix[s])
    d  <- suppressMessages(nhanes(qname))
    if (is.null(d))
      next
    
    d$year <- yrs[s]
    
    if (is.null(out)) {
      out <-
        as_tibble(d) %>% mutate_if(is.factor, as.character.factor) %>% 
        mutate_if(is.integer, as.character)
      labs <- get_labs(out, d)
    } else{
      labs <- get_labs(out, d)
      out <-
        out %>% bind_rows(
          d %>% mutate_if(is.factor, as.character.factor) %>% 
            mutate_if(is.integer, as.character)
        )
    }
    update <- rep('', ncol(out))
    names(update) <- colnames(out)
    update[names(labs)] <- labs
    label(out, self = FALSE) <- update
  }
  
  if (translate) {
    if (!is.null(type)) {
      d_vars <- NULL
      for (s in seq_along(suffix)) {
        qname <- paste0(query, suffix[s])
        d_vars_tmp  <-
          try(nhanesTableVars(type, qname, namesonly = TRUE), silent = TRUE)
        if (class(d_vars_tmp) == 'try-error')
          next
        update <- setdiff(d_vars_tmp, d_vars)
        if (length(update) > 0) {
          d_vars <- c(update, d_vars)
          out <-
            suppressWarnings(nhanesTranslate(qname, d_vars, data = out))
        }
      }
    }
  }
  
  return(out)
}


opioids <- c(
  'CODEINE',
  'OXYCODONE',
  'TRAMADOL',
  'MORPHINE',
  'HYDROMORPHONE',
  'FENTANYL',
  'CARFENTANIL',
  'PROPOXYPHENE',
  'HYDROCODONE',
  'HEROIN',
  'PENTAZOCINE',
  'DIHYDROCODEINE',
  'MEPERIDINE',
  'TAPENTADOL',
  'OPIUM'
) # 'BUPRENORPHINE','NALOXONE'
find_drugs <- function(rxs, lookup) {
  lookup <- paste0('\\<', opioids, '\\>')
  hits <- vector(length = length(rxs))
  for (i in seq_along(rxs)) {
    r <- rxs[i]
    if (is.na(r) | r == '')
      next
    for (l in lookup) {
      if (grepl(l, r)) {
        hits[i] <- TRUE
        next
      }
    }
  }
  return(as.integer(hits))
}
```


# Load and Prepare Data

```{r, comment=FALSE, warning=FALSE, results=FALSE, tidy=TRUE, message=FALSE}
dat <-
  readRDS('D:/Downloads/substance_use_analysis/tifdata_paper.rds')

subtract <- function(x, y)
  x - y
cancerdx <- dat$cancer %>%
  select(SEQN, year, starts_with('MCQ240')) %>%
  left_join(dat$demo %>% select(SEQN, year, age = RIDAGEYR),
            by = c('SEQN', 'year')) %>%
  mutate_if(is.factor, as.character.factor) %>%
  mutate_at(vars(starts_with('MCQ240')),
            ~ ifelse(. == "Don't know" | . == '99999' | . == '77777', NA, .)) %>%
  mutate_at(vars(starts_with('MCQ240')),  ~ ifelse(. == '80 years or older', '9999', .)) %>%
  mutate_at(vars(starts_with('MCQ240')), as.integer) %>%
  mutate(age = as.integer(age)) %>%
  mutate_at(vars(starts_with('MCQ240')),  ~ subtract(age, .)) %>%
  mutate_at(vars(starts_with('MCQ240')),  ~ ifelse(. < 1, 1, 0)) %>%
  mutate(cancer1yr = rowSums(select(., starts_with('MCQ240')), na.rm = TRUE)) %>%
  filter(cancer1yr > 0) %>%
  select(SEQN, year, cancer1yr)

opioids <- dat$druginfo %>%
  filter(
    RXDDCI1A == '57' & RXDDCI1B == '58' & RXDDCI1C %in% c('60', '191') |
      RXDDCI2A == '57' &
      RXDDCI2B == '58' & RXDDCI2C %in% c('60', '191') |
      RXDDCI3A == '57' &
      RXDDCI3B == '58' & RXDDCI3C %in% c('60', '191')
  ) %>%
  select(id = RXDDRGID, drug = RXDDRUG)
# filter(!grepl('NALOXONE|BUPRENORPHINE',drug))


drugusers <- dat$otherdruguse %>%
  select(
    SEQN,
    year,
    starts_with('DUQ270'),
    starts_with('DUQ350'),
    starts_with('DUQ310'),
    starts_with('DUQ400'),
    DUQ240,
    DUQ250,
    DUQ290,
    DUQ330,
    DUQ370
  ) %>%
  filter(DUQ240 %in% c('Yes', 'No')) %>%
  # filter_at(vars(DUQ250,DUQ290,DUQ330,DUQ370),all_vars(. %in% c('Yes','No'))) %>%
  mutate_at(vars(ends_with('Q')), as.numeric) %>%
  mutate_at(vars(ends_with('Q')),  ~ ifelse(. == 7777 |
                                              . == 9999, NA, .)) %>%
  # filter_at(vars(ends_with('Q')),any_vars(!is.na(.))) %>%
  mutate(
    days_cocaine = case_when(
      DUQ270U == 'Days' ~ DUQ270Q,
      DUQ270U == 'Weeks' ~ DUQ270Q * 7,
      DUQ270U == 'Months' ~ DUQ270Q * 30,
      DUQ270U == 'Year' ~ DUQ270Q * 365
    ),
    days_heroin = case_when(
      DUQ310U == 'Days' ~ DUQ310Q,
      DUQ310U == 'Weeks' ~ DUQ310Q * 7,
      DUQ310U == 'Months' ~ DUQ310Q * 30,
      DUQ310U == 'Year' ~ DUQ310Q * 365
    ),
    days_meth = case_when(
      DUQ350U == 'Days' ~ DUQ350Q,
      DUQ350U == 'Weeks' ~ DUQ350Q * 7,
      DUQ350U == 'Months' ~ DUQ350Q * 30,
      DUQ350U == 'Year' ~ DUQ350Q * 365
    ),
    days_iv = case_when(
      DUQ400U == 'Days' ~ DUQ400Q,
      DUQ400U == 'Weeks' ~ DUQ400Q * 7,
      DUQ400U == 'Months' ~ DUQ400Q * 30,
      DUQ400U == 'Year' ~ DUQ400Q * 365
    )
  ) %>%
  rowwise() %>%
  mutate(drugdur = min(days_cocaine, days_heroin, days_meth, days_iv, na.rm =
                         TRUE)) %>%
  ungroup() %>%
  mutate(
    drugdurcat = case_when(
      drugdur <= 365 ~ '<1y',
      drugdur > 365 & drugdur < Inf ~ '>1y',
      DUQ240 == 'No' |
        (DUQ250 == 'No' &
           DUQ290 == 'No' & DUQ330 == 'No' & DUQ370 == 'No') ~ 'none'
    )
  ) %>%
  # filter(!is.na(drugdurcat)) %>%
  mutate(druguse = ifelse(drugdurcat == 'none', 'No', 'Yes')) %>%
  select(SEQN, year, druguse, drugdur, drugdurcat, starts_with('days'))


opioidusers <- dat$druguse %>%
  select(
    SEQN,
    year,
    rxcount = RXD295,
    rxuse = RXDUSE,
    rx = RXDDRUG,
    rxid = RXDDRGID,
    rxdur = RXDDAYS
  ) %>%
  # filter(opioiduse %in% c('Yes','No')) %>%
  mutate(
    opioiduse = case_when((rxid %in% opioids$id) ~ 'Yes',!(rxid %in% opioids$id) |
                            rxuse == 'No' ~ 'No'
    ),
    opioiddur = ifelse(opioiduse == 'Yes', as.integer(rxdur), NA),
    opioiddurcat = case_when(
      opioiduse == 'No' ~ 'none',
      opioiddur < 90 ~ 'short',
      opioiddur >= 90 &
        opioiddur <= 25550 ~ 'long'
    )
  ) %>%
  mutate(
    rxcount = as.integer(rxcount),
    rxcount_listed = str_count(as.character.factor(rx), ';')
  )


opioidusers <- dat$druguse %>%
  select(
    SEQN,
    year,
    rxcount = RXD295,
    rxuse = RXDUSE,
    rx = RXDDRUG,
    rxid = RXDDRGID,
    rxdur = RXDDAYS
  ) %>%
  # filter(opioiduse %in% c('Yes','No')) %>%
  mutate(
    opioiduse = case_when((rxid %in% opioids$id) ~ 'Yes',!(rxid %in% opioids$id) |
                            rxuse == 'No' ~ 'No'
    ),
    opioiddur = ifelse(opioiduse == 'Yes', as.integer(rxdur), NA),
    rxcount = as.integer(rxcount),
    rxcount_listed = str_count(as.character.factor(rx), ';'),
    rxcount_listed = ifelse(
      nchar(as.character.factor(rx)) > 0,
      rxcount_listed + 1,
      rxcount_listed
    )
  ) %>%
  group_by(SEQN, year) %>%
  mutate(
    rxcount_listed = sum(rxcount_listed),
    opioiduse = ifelse(any(opioiduse == 'Yes'), 'Yes', opioiduse),
    opioiddur = ifelse(opioiddur == 99999 |
                         opioiddur == 77777, NA, opioiddur),
    opioiddur = max(opioiddur, na.rm = TRUE),
    opioiddur = ifelse(is.infinite(opioiddur), NA, opioiddur)
  ) %>%
  ungroup() %>%
  nest(rx = c(rx, rxdur, rxid)) %>%
  mutate(
    opioiddurcat = case_when(
      opioiduse == 'No' ~ 'none',
      opioiddur < 90 ~ 'short',
      opioiddur >= 90 &
        opioiddur <= 25550 ~ 'long'
    )
  )


users <- full_join(drugusers, opioidusers, by = c('SEQN', 'year')) %>%
  filter((druguse %in% c('Yes', 'No')) |
           (opioiduse %in% c('Yes', 'No')),!is.na(druguse) |
           !is.na(opioiduse)) %>%
  left_join(
    dat$smoke %>% # might be wrong
      select(SEQN, year, smokecurrent = SMQ040, smokelife = SMQ020) %>%
      mutate(
        smoke = case_when(
          smokecurrent %in% c('Every day,', 'Some days, or') ~ 'Current',
          smokelife == 'Yes' ~ 'Former',
          smokecurrent == 'Not at all?' |
            smokelife == 'No' ~ 'Never'
        )
      ) %>%
      select(SEQN, year, smoke),
    by = c('SEQN', 'year')
  ) %>%
  left_join(
    dat$ins %>%
      select(SEQN, year, ins1 = HID010, ins2 = HIQ011) %>%
      mutate(
        ins = case_when(ins1 == 'Yes' | ins2 == 'Yes' ~ 'Yes',
                        ins1 == 'No' |
                          ins2 == 'No' ~ 'No')
      ) %>%
      select(SEQN, year, ins),
    by = c('SEQN', 'year')
  ) %>%
  left_join(
    dat$demo %>% select(
      SEQN,
      year,
      age = RIDAGEYR,
      sex = RIAGENDR,
      race = RIDRETH1,
      edu = DMDEDUC2
    ) %>%
      mutate(
        age = as.integer(age),
        edu = case_when(
          edu %in% c('Less Than 9th Grade',
                     '9-11th Grade (Includes 12th grad') ~ 'Less than high school' ,
          edu == 'High School Grad/GED or Equivale' ~ 'High school or equivalent',
          edu == 'Some College or AA degree' ~ 'Some college',
          edu == 'College Graduate or above' ~ 'College or higher'
        ),
        race = case_when(
          race %in% c('Mexican American', 'Other Hispanic') ~ 'Hispanic',
          race == 'Other Race - Including Multi-Rac' ~ 'Non-Hispanic Other',
          race == 'Non-Hispanic White' ~ 'Non-Hispanic White',
          race == 'Non-Hispanic Black' ~ 'Non-Hispanic Black'
        )
      ),
    by = c('SEQN', 'year')
  ) %>%
  left_join(
    dat$demo_raw %>% select(
      SEQN,
      cycle = SDDSRVYR,
      year,
      wtint2yr = WTINT2YR,
      wtmec2yr = WTMEC2YR,
      cluster = SDMVPSU,
      strata = SDMVSTRA
    ),
    by = c('year', 'SEQN')
  ) %>%
  filter(age >= 18 & age <= 100) %>%
  left_join(dat$body %>% select(SEQN, year, bmi = BMXBMI), by = c('SEQN', 'year')) %>%
  mutate(
    bmicat = case_when(
      bmi < 20 ~ 'underweight',
      bmi >= 20 & bmi < 25 ~ 'normal',
      bmi >= 25 & bmi < 30 ~ 'overweight',
      bmi >= 30 & bmi < 35 ~ 'obese I',
      bmi >= 35 & bmi < 40 ~ 'obese II',
      bmi >= 40 & bmi <= 80 ~ 'obese III'
    ),
    agecat = case_when(
      age >= 18 & age < 25 ~ '18-24',
      age >= 25 & age < 35 ~ '25-34',
      age >= 35 & age < 45 ~ '35-44',
      age >= 45 & age < 55 ~ '45-54',
      age >= 55 & age < 65 ~ '55-64',
      age >= 65 & age < 75 ~ '65-74',
      age >= 75 & age < 100 ~ '75-100'
    )
  ) %>%
  left_join(dat$preg %>% select(SEQN, year, preg = RHD143),
            by = c('SEQN', 'year')) %>%
  mutate(preg = case_when(preg == 'Yes' ~ 'Yes', TRUE ~ 'No')) %>%
  left_join(cancerdx, by = c('SEQN', 'year')) %>%
  filter(preg != 'Yes' | is.na(preg)) %>%
  filter(is.na(cancer1yr)) %>%
  filter(!is.na(smoke)) %>%
  filter(!is.na(edu)) %>%
  filter(ins %in% c('Yes', 'No')) %>%
  mutate(
    sex = relevel(as.factor(sex), ref = 'Male'),
    opioiddurcat = relevel(as.factor(opioiddurcat), ref = 'none'),
    drugdurcat = relevel(as.factor(drugdurcat), ref = 'none'),
    bmicat = relevel(as.factor(bmicat), ref = 'normal'),
    agecat = relevel(as.factor(agecat), ref = '35-44'),
    race = relevel(as.factor(race), ref = 'Non-Hispanic White'),
    edu = relevel(as.factor(edu), ref = 'High school or equivalent'),
    ins = relevel(as.factor(ins), ref = 'No'),
    smoke = relevel(as.factor(smoke), ref = 'Never'),
    yearcat = relevel(as.factor(year), ref = '2003')
  ) %>%
  mutate(
    strata = dense_rank(strata),
    cluster = dense_rank(cluster),
    opioiddurrank = case_when(
      opioiddurcat == 'none' ~ 1,
      opioiddurcat == 'short' ~ 2,
      opioiddurcat == 'long' ~ 3
    )
  ) %>%
  select(
    SEQN,
    year,
    yearcat,
    bmi,
    bmicat,
    age,
    agecat,
    sex,
    race,
    edu,
    ins,
    smoke,
    strata,
    cluster,
    rx,
    rxcount,
    rxcount_listed,
    drugdur,
    drugdurcat,
    druguse,
    starts_with('days'),
    opioiddur,
    opioiddurcat,
    opioiddurrank,
    opioiduse,
    wtint2yr,
    wtmec2yr
  ) %>%
  mutate(wtintadj = wtint2yr / length(unique(year)),
         wtmecadj = wtmec2yr / length(unique(year)))


dat_everything <- readRDS('/Research/Tiffany/dat_everything.rds')
dat_everything <- dat_everything %>%
  select(
    union(
      dat_everything %>%
        filter(SEQN %in% (
          users %>% filter(opioiduse == 'Yes') %>% select(SEQN) %>% distinct() %>% unlist()
        )) %>%
        select_if( ~ sum(!is.na(.)) > 100) %>% # consider changing
        colnames(),
      dat_everything %>%
        filter(SEQN %in% (
          users %>% filter(druguse == 'Yes') %>% select(SEQN) %>% distinct() %>% unlist()
        )) %>%
        select_if( ~ sum(!is.na(.)) > 100) %>% # consider changing
        colnames()
    )
  ) %>%
  select(-BMXBMI) %>%
  mutate_if(is.factor, as.character.factor) %>%
  mutate_all( ~ ifelse(. %in% c('Refused', "Don't know"), NA, .))

users_everything <- users %>%
  left_join(dat_everything, by = c('SEQN', 'year')) %>%
  rename(
    normal_otoscopy_L = AUXOTSPL,
    normal_otoscopy_R = AUXROTSP,
    middle_ear_pres_R = AUXTMEPR,
    middle_ear_pres_L = AUXTMEPL,
    tympanogram_qual_R = AUAREQC,
    tympanogram_qual_L = AUALEQC,
    hear_gen = AUQ130,
    hear_last_test = AUQ140,
    hear_aid = AUQ150,
    hear_recent_sx = AUQ190,
    pulse = BPXPLS,
    bp_sys_1 = BPXSY1,
    bp_sys_2 = BPXSY2,
    bp_sys_3 = BPXSY3,
    bp_sys_4 = BPXSY4,
    bp_di_1 = BPXDI1,
    bp_di_2 = BPXDI2,
    bp_di_3 = BPXDI3,
    bp_di_4 = BPXDI4,
    bp_high = BPQ020,
    bp_med = BPQ040A,
    chol_high = BPQ080,
    chol_med = BPQ090D,
    wt = BMXWT,
    ht = BMXHT,
    overweight1 = MCQ080,
    overweight2 = MCQ160J,
    feno = ENXMEAN,
    fev1_bl = SPXNFEV1,
    fet_bl = SPXNFET,
    fvc_bl = SPXNFVC,
    vis_R = VIDRVA,
    vis_L = VIDLVA,
    trouble_seeing = MCQ140,
    vis_acuity_R = VIDROVA,
    vis_acuity_L = VIDLOVA,
    gen_health1 = HSD010,
    days_in_month_poor_health = HSQ470,
    days_in_month_poor_mental = HSQ480,
    days_in_month_forced_inactive = HSQ490,
    cp = CDQ001,
    cp_exert = CDQ002,
    cp_noexert = CDQ003,
    cp_severe30 = CDQ008,
    sob_stairs = CDQ010,
    dm = DIQ010,
    dm_insulin = DIQ050,
    dm_med = DIQ070,
    dm_eye = DIQ080,
    dm_ulcer = DIQ090,
    dm_numb_recent_handfeet = DIQ100,
    dm_numb_loc = DIQ110,
    dm_paintingle_recent_handfeet = DIQ120,
    dm_paintingle_loc = DIQ130,
    dm_pain_leg = DIQ140,
    dm_pain_calf = DIQ150,
    run_out_food = FSD032A,
    emo_support = SSQ011,
    hepa_vax = IMD010,
    hepb_vax = IMQ020,
    liverdz1 = MCQ160L,
    liverdz2 = MCQ170L,
    liverdz_age = MCQ180L,
    liver_cap_med = LUXCAPM,
    liver_cap_iqr = LUXCPIQR,
    pneumo_vax = IMQ030,
    asthma = MCQ010,
    asthma_recent_treatment = MCQ053,
    asthma_recent_attack = MCQ040,
    asthma_recent_er = MCQ050,
    emphysema = MCQ160G,
    emphysema_age = MCQ180G,
    chr_bronch1 = MCQ160K,
    chr_bronch2 = MCQ170K,
    chr_bronch_age = MCQ180K,
    copd = MCQ160O,
    cough_chronic = RDQ031,
    cough_prod = RDQ050,
    wheeze = RDQ070,
    wheeze_med = RDQ134,
    cough_nocturnal_dry = RDQ140,
    blood_trans = MCQ092,
    arthritis = MCQ160A,
    arthritis_age = MCQ180A,
    gout = MCQ160N,
    gout_age = MCQ180N,
    fx_hip = OSQ010A,
    fx_wrist = OSQ010B,
    fx_spine = OSQ010C,
    op = OSQ060,
    op_tx = OSQ070,
    chf = MCQ160B,
    chf_age = MCQ180B,
    chd = MCQ160C,
    chd_age = MCQ180C,
    angina = MCQ160D,
    angina_age = MCQ180D,
    mi = MCQ160E,
    mi_age = MCQ180E,
    stroke = MCQ160F,
    stroke_age = MCQ180F,
    thyroiddz1 = MCQ160M,
    thyroiddz2 = MCQ160I,
    thyroiddz_current = MCQ170M,
    thyroiddz_age = MCQ180M,
    goiter = MCQ160H,
    cancer = MCQ220,
    cancer_type = MCQ230A,
    dentist_last_visit = OHQ030,
    insecure_mouth_freq = OHQ630,
    insecure_mouth_freq_recent = OHQ680,
    dentist_could_not_get_recent = OHQ770,
    herpes = SXQ260,
    warts = SXQ265,
    gono = SXQ270,
    chlam = SXQ272,
    hysterectomy = RHD280,
    gen_health2 = HUQ010,
    gen_health_comp = HUQ020,
    hc_loc = HUQ030,
    hc_type = HUQ040,
    hc_count = HUQ050,
    hc_last = HUQ060,
    hosp_nights = HUQ071,
    hosp_nights_count = HUD080,
    mental_visit_count = HUQ090,
    activity_walkbike = PAD020,
    activity_avg_amount = PAQ180,
    smoke_age_reg = SMD055,
    smoke_age = SMD030,
    smoke_num_cigs_per_day_now = SMD070,
    smoke_num_cigs_per_day_now_length = SMD075,
    smoke_num_cigs_per_day = SMD057,
    smoke_avg_cigs_per_day_recent = SMD650,
    smoke_100cigs = SMQ020
  ) %>%
  mutate(
    gen_health1 = gsub(',.*|\\?.*', '', gen_health1, ignore.case = TRUE),
    gen_health2 = gsub(',.*|\\?.*', '', gen_health2, ignore.case =
                         TRUE),
    dm = relevel(factor(dm, ordered = FALSE), ref = 'No'),
    gen_health1 = factor(gen_health1, ordered = TRUE, levels = rev(
      c('Excellent', 'Very good', 'Good', 'Fair', 'Poor')
    )),
    gen_health2 = factor(gen_health2, ordered = TRUE, levels = rev(
      c('Excellent', 'Very good', 'Good', 'Fair', 'Poor')
    )),
    bmicat = factor(
      bmicat,
      ordered = TRUE,
      levels = c(
        'underweight',
        'normal',
        'overweight',
        'obese I',
        'obese II',
        'obese III'
      )
    ),
    agecat = factor(
      agecat,
      ordered = TRUE,
      levels = c('18-24', '25-34', '35-44', '45-54', '55-64', '65-74', '75-100')
    ),
    edu = factor(
      edu,
      ordered = TRUE,
      levels = c(
        'Less than high school',
        'High school or equivalent',
        'Some college',
        'College or higher'
      )
    ),
    yearrank = dense_rank(year),
    bmirank = dense_rank(bmicat),
    edurank = dense_rank(edu),
    agerank = dense_rank(agecat)
  ) %>%
  mutate_at(vars(starts_with('bp_sys')), as.integer) %>%
  mutate_at(vars(starts_with('bp_di')), as.integer) %>%
  rowwise() %>%
  mutate(map_mean = mean(c((bp_sys_1 + 2 * bp_di_1) / 3,
                           (bp_sys_2 + 2 * bp_di_2) / 3,
                           (bp_sys_3 + 2 * bp_di_3) / 3
  ), na.rm = TRUE),
  map_min = min(c((bp_sys_1 + 2 * bp_di_1) / 3,
                  (bp_sys_2 + 2 * bp_di_2) / 3,
                  (bp_sys_3 + 2 * bp_di_3) / 3
  ), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate_at(vars(starts_with('map')),  ~ ifelse(is.infinite(.) |
                                                  is.nan(.), NA, .))
```

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
users_everything %>%
  filter(!is.na(hc_loc),!is.na(drugdurcat),!is.na(ins),!is.na(race)) %>%
  group_by(race, drugdurcat, ins, hc_loc) %>%
  dplyr::summarize(f = sum(wtintadj)) %>%
  mutate(f = f / sum(f)) %>%
  ggplot(aes(x = drugdurcat, y = f, fill = hc_loc)) +
  geom_col(color = 'black') +
  coord_flip() +
  facet_grid(race ~ ins) +
  th +
  labs(y = '',
       x = 'Time Since Drug Use',
       fill = 'Healthcare Location',
       title = 'Health Insurance')

users_everything %>%
  filter(!is.na(hc_loc),!is.na(opioiddurcat),!is.na(ins),!is.na(race)) %>%
  group_by(race, opioiddurcat, ins, hc_loc) %>%
  dplyr::summarize(f = sum(wtintadj)) %>%
  mutate(f = f / sum(f)) %>%
  ggplot(aes(x = opioiddurcat, y = f, fill = hc_loc)) +
  geom_col(color = 'black') +
  coord_flip() +
  facet_grid(race ~ ins) +
  th +
  labs(y = '',
       x = 'Duration Using Opioids',
       fill = 'Healthcare Location',
       title = 'Health Insurance')


users_everything %>%
  filter(!is.na(rxcount_listed),!is.na(opioiddurcat),!is.na(ins),!is.na(agecat)) %>%
  group_by(opioiddurcat, ins, agecat) %>%
  dplyr::summarize(mean = sum(wtintadj * rxcount_listed, na.rm = TRUE) /
                     sum(wtintadj, na.rm = TRUE)) %>%
  ggplot(aes(x = opioiddurcat, y = mean)) +
  geom_col(color = 'black') +
  coord_flip() +
  facet_grid(agecat ~ ins) +
  th +
  labs(y = 'Average Number of Opioids',
       x = 'Duration Using Opioids',
       fill = 'Healthcare Location',
       title = 'Health Insurance')

users_everything %>%
  filter(!is.na(rxcount_listed),!is.na(drugdurcat),!is.na(ins),!is.na(agecat)) %>%
  group_by(drugdurcat, ins, agecat) %>%
  dplyr::summarize(mean = sum(wtintadj * rxcount_listed, na.rm = TRUE) /
                     sum(wtintadj, na.rm = TRUE)) %>%
  ggplot(aes(x = drugdurcat, y = mean)) +
  geom_col(color = 'black') +
  coord_flip() +
  facet_grid(agecat ~ ins) +
  th +
  labs(y = 'Average Number of Opioids',
       x = 'Time Since Drug Use',
       fill = 'Healthcare Location',
       title = 'Health Insurance')

users_everything %>%
  filter(!is.na(opioiddurcat),
         !is.na(bp_med)) %>%
  distinct() %>%
  group_by(ins,sex,bp_high,opioiddurcat,bp_med) %>%
  dplyr::summarize(f=sum(wtmecadj)) %>%
  mutate(f=f/sum(f)) %>%
  ggplot(aes(x=opioiddurcat,y=f,fill=bp_med)) +
  geom_col(color='black') +
  coord_flip() +
  facet_grid(~sex+ins) +
  th +
    labs(y = 'Proportion of Subjects',
       x = 'Duration Using Opioids',
       fill = 'On BP Med.',
       title = 'Sex vs Health Insurance')
```

A few sanity checks. First, the impact on a bunch of predictors on chest pain.
We're basically controlling for sex, race, age, education, insurance, smoking,
year surveyed, and bmi, and then focusing on the impact that the duration of
opioid use (short vs long) has on chest pain. I'm using a package that accounts
for survey designs as well, with the appropriate weighting. I'd prefer to do
this fully Bayesian with post stratification (see the one script), but that's
for down the road once we identify some questions of interest and, by extension,
interesting analyses designs.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      cp,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      drugdurcat
    ) %>%
    filter(!is.na(cp), !is.na(bmirank), !is.na(drugdurcat)) %>%
    mutate(cp = as.integer(ifelse(cp == 'Yes', 1, 0))) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    cp ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + drugdurcat,
    design = svy,
    family = binomial(link = 'logit'),
    rescale = TRUE
  )
summary(m)
```

Both opioid durations affect the frequency chest pain was reported. The estimate
is over twice as large for long durations (> 90 days), suggesting that the 
longer you're on opioids, the more likely you are to report chest pain, which is 
reasonable.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      bp_high,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      opioiddurcat
    ) %>%
    filter(!is.na(bp_high),!is.na(bmirank),!is.na(opioiddurcat)) %>%
    mutate(bp_high = as.integer(ifelse(bp_high == 'Yes', 1, 0))) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    bp_high ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + opioiddurcat,
    design = svy,
    family = binomial(link = 'logit'),
    rescale = TRUE
  )
summary(m)
```

Here, only long term opioid use is associated with reporting high blood pressure.
The effect is less than what we saw for chest pain, too.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      bp_high,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      drugdurcat
    ) %>%
    filter(!is.na(bp_high), !is.na(bmirank), !is.na(drugdurcat)) %>%
    mutate(bp_high = as.integer(ifelse(bp_high == 'Yes', 1, 0))) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    bp_high ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + drugdurcat,
    design = svy,
    family = binomial(link = 'logit'),
    rescale = TRUE
  )
summary(m)
```

Now we're looking at whether recreational drug use affects the frequency in which
people reported high blood pressure, which it doesn't. Taking drugs within the
past year (<1y) has no effect.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      dm,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      opioiddurcat
    ) %>%
    mutate(dm = case_when(dm == 'No' ~ 0, dm == 'Yes' ~ 1)) %>%
    filter(!is.na(dm), !is.na(bmirank), !is.na(opioiddurcat)) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    dm ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + opioiddurcat,
    design = svy,
    family = binomial(link = 'logit'),
    rescale = TRUE
  )
summary(m)
```

Here's the effect that long and short term opioid use has on presence of DM. Only
long term opioid use impacts DM reporting, and the size of the effect is less 
than what we saw for chest pain.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      dm,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      drugdurcat
    ) %>%
    mutate(dm = case_when(dm == 'No' ~ 0, dm == 'Yes' ~ 1)) %>%
    filter(!is.na(dm), !is.na(bmirank), !is.na(drugdurcat)) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    dm ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + drugdurcat,
    design = svy,
    family = binomial(link = 'logit'),
    rescale = TRUE
  )
summary(m)
```

And here it shows that recreational drug use has no impact on DM reporting.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      gen_health1,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      drugdurcat
    ) %>%
    filter(!is.na(gen_health1), !is.na(bmirank), !is.na(drugdurcat)) %>%
    mutate(gen_health1 = dense_rank(gen_health1)) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    gen_health1 ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + drugdurcat,
    design = svy,
    rescale = TRUE
  )
summary(m)
```

Nor does it affect a person's view of their general health.

```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
svy <- svydesign(
  id =  ~ cluster,
  strata =  ~ strata,
  weights =  ~ wtmecadj,
  data = users_everything %>%
    select(
      SEQN,
      gen_health1,
      sex,
      race,
      agerank,
      edurank,
      ins,
      smoke,
      yearrank,
      bmirank,
      wtmecadj,
      cluster,
      strata,
      opioiddurcat
    ) %>%
    filter(!is.na(gen_health1), !is.na(bmirank), !is.na(opioiddurcat)) %>%
    mutate(gen_health1 = dense_rank(gen_health1)) %>%
    distinct(),
  nest = TRUE
)
m <-
  svyglm(
    gen_health1 ~ sex + race + agerank + edurank + ins + smoke + yearrank + bmirank + opioiddurcat,
    design = svy,
    rescale = TRUE
  )
summary(m)
```

But opioids do, in that opioid is inversely associated with a person's view of
their general health, so if one uses opioids, they're more likely to have a more
negative view of their health, and the degree of the relationship is greater
with a longer duration of opioid use.


```{r, comment=FALSE, warning=FALSE, results=TRUE, tidy=TRUE, message=FALSE, fig.width=10, fig.height=7}
plot_vars('opioiddurcat',
          'cp',
          data = users_everything,
          vars = c('ins', 'sex')) +
  th +
  labs(y = '',
       x = 'Duration Using Opioids',
       title = 'Sex vs Insurance',
       fill = 'CP')

plot_vars('opioiddurcat',
          'bp_high',
          data = users_everything,
          vars = c('ins', 'sex')) +
  th +
  labs(y = '',
       x = 'Duration Using Opioids',
       title = 'Sex vs Insurance',
       fill = 'High BP')

plot_vars('drugdurcat',
          'bp_high',
          data = users_everything,
          vars = c('ins', 'sex')) +
  th +
  labs(y = '',
       x = 'Time Since Drug Use',
       title = 'Sex vs Insurance',
       fill = 'High BP')

plot_vars('drugdurcat',
          'bp_high',
          data = users_everything,
          vars = c('ins', 'sex')) +
  th +
  labs(y = '',
       x = 'Time Since Drug Use',
       title = 'Sex vs Insurance',
       fill = 'High BP')

plot_vars('opioiddurcat',
          'dm',
          data = users_everything,
          vars = c('ins', 'sex', 'bmicat')) +
  th +
  labs(y = '',
       x = 'Duration Using Opioids',
       title = 'Sex vs Insurance',
       fill = 'DM')

plot_vars('drugdurcat',
          'dm',
          data = users_everything,
          vars = c('ins', 'sex', 'bmicat')) +
  th +
  labs(y = '',
       x = 'Time Since Drug Use',
       title = 'Sex vs Insurance',
       fill = 'DM')
```